\documentclass[a4paper]{resume} % Use the custom resume.cls style
\usepackage[T1]{fontenc}
\usepackage{helvet}

%\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\begin{document}

\begin{center}
    \MakeUppercase{\huge \textbf{David Figueiredo}}\\
    Backend developer (.NET \& Python)
\end{center}

%----------------------------------------------------------------------------------------
%	BIO
%----------------------------------------------------------------------------------------
 
\begin{rSection}{Bio}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}}l}
    E-mail      & d.figueiredo@outlook.pt               \\  
    Phone       & (+351) 914156449                      \\
    LinkedIn    & linkedin.com/in/davidfigueiredo31     \\
    GitHub      & github.com/dfigueiredo31              \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Summary
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
    Developer with 4 years experience working in complex and fast-paced environments. Solid foundations in .NET Framework, C\#, APIs and Webservices (ASMX, WCF), with exposure to Python through a teaching role in higher education. Team player with strong analytic and critic sense. Currently looking for backend, AI or cloud role.
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

% 4 input arguments - job title, year(s) employed, company and location
\begin{rSubsection}{Assistant Professor}{Fev 2025 - Jul 2025}{Universidade de Trás-os-Montes e Alto Douro}{}

    \item Lectured a Computer Lab on Python, aimed at 1st cycle/undergrad students.
    
    \item Covered introductory topics such as:
        \begin{list}{$\cdot$}{}
		      \setlength{\itemsep}{-0.5em} \vspace{-0.5em}
            \item Programming logic and basic algorithms
            \item Control structures
            \item Basic data structures: variables, lists, dictionaries, sets and tuples
            \item Importance of good programming practices such as readable, reusable and documented code
	    \end{list}
        
\end{rSubsection}

\vspace{1em}

\begin{rSubsection}{Application Management Services (AMS) Consultant}{Oct 2022 - May 2025}{Softinsa - Engenharia de Software Avançado, Lda.}{}

    \item Maintained and implemented Costumer Communication workflows, for a client in the banking sector.
    
    \item Tools:
        \begin{list}{$\cdot$}{}
		      \setlength{\itemsep}{-0.5em} \vspace{-0.5em}
            \item WCF and ASMX webservices built on .NET Framework (C\#)
            \item SQL Server
            \item Azure DevOps
            \item Precisely EngageOne software suit
	    \end{list}
    
\end{rSubsection}

\vspace{1em}

\begin{rSubsection}{Interoperability Engineer}{May 2021 - Oct 2022}{ST+I Unipessoal Lda.}{}
    
    \item Assisted in the development of interoperability capabilities for a healthcare software company, by developing and maintaining HL7 interfaces and REST APIs using ASP.NET, C\#, and Visual Basic.
    
        \item Tools:
        \begin{list}{$\cdot$}{}
		      \setlength{\itemsep}{-0.5em} \vspace{-0.5em}
            \item .NET Framework (C\# and VB)
            \item Oracle SQL
            \item SVN
	    \end{list}

\end{rSubsection}

\vspace{1em}

\begin{rSubsection}{Web Developer}{May 2020 - May 2021}{S. Roque - Máquinas e Tecnologia Laser, S.A.}{}  

    \item Assisted in the development of the company’s intranet portal.
    \item Tools:
        \begin{list}{$\cdot$}{}
		      \setlength{\itemsep}{-0.5em} \vspace{-0.5em}
            \item Backend: ASP.NET MVC, C\#, Entity Framework, MS SQL Server
            \item Frontend: Razor pages, Bootstrap, jQuery
	    \end{list}

\end{rSubsection}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

    \begin{rSubsection}{Master's Degree in Engineering and Management of Information Systems}{2023}{University of Minho}{Portugal}
        %\item Master's thesis - Risk management in HIS interoperability (https://hdl.handle.net/1822/84012)
    \end{rSubsection}
    
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Skills}
%
%    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%        Languages       & C\#, Visual Basic, Python (Academic), Java (Academic)             \\
%        Web Services    & WCF, ASMX, REST APIs                                              \\
%        Frameworks      & .NET Framework, ASP.NET, ASP.NET MVC                              \\
%        Tools           & Precisely EngageOne, Entity Framework, MS SQL Server, Azure, Git, SVN  \\
%        Frontend        & Razor Pages, Bootstrap, jQuery                                    \\
%    \end{tabular}
%    
%\end{rSection}
%

\end{document}
